Co-citations in context

### 2019-05-27 cocit_r.tex
edited author contributions

\authorcontributions 
This study was designed by GD, JB, SD, and TW. Simulations and analysis were performed by AD, GC, JB, and SD. Infrastructure, and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.  All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.

>>>>

\authorcontributions 
This study was designed by GC, JB, SD, and TW. Simulations and analysis were performed by AD, GC, JB, and SD. Infrastructure and workflows used to generate data used in this study were developed by AD, DK, SL, SD, and GC.  All authors reviewed and commented on the manuscript, which was written by GC, JB, and TW.
